Age-related changes in plant growth and traits

### 2016-12-13 ms/Accessory/Wenk-Accessory-SI.Rnw
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

flowering_parts <- read.csv("ms/Accessory/Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)

@@

  #plot(graph)
  plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE)
  box()
}
@

@@

<<echo=FALSE,results='asis'>>=
TableSXX <- read.csv("Table_SXX_propagule_invest_vs_repro_inv.csv",
                    stringsAsFactors=FALSE, check.names=FALSE)

names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
TableSXX[,4] <- format_p(TableSXX[,4])
TableSXX[,7] <- format_p(TableSXX[,7])

@@

<<echo=FALSE,results='asis'>>=
TableSXX <- read.csv("Table_SXX_propagule_invest_vs_repro_inv.csv",
                    stringsAsFactors=FALSE, check.names=FALSE)

names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
TableSXX[,4] <- format_p(TableSXX[,4])
TableSXX[,7] <- format_p(TableSXX[,7])

<<echo=FALSE,results='asis'>>=
Table02 <- read.csv("Table02_acc_cost_embryo_size_slopes.csv",
                    stringsAsFactors=FALSE, check.names=FALSE)

names(Table02) <- c("Variable", "r$^2$", "slope (95 CI)","p$_{slope<>1}$")
Table02[,2] <- format(Table02[,2],digits=2,nsmall=2)
Table02[,4] <- format(Table02[,4],digits=4,nsmall=4)

print(xtable(Table02,
               hline.after=c(1),
               align='p{0.1cm}p{4cm}p{1cm}p{3cm}p{1cm}',
               caption="Correlations with total reproductive investment"),
               sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = TRUE
        , size = "small"
        , floating = FALSE)
@

Table 2. Scaling of reproductive tissue costs with seed size. All variables were showed a strong correlation with seed size (p < 0.0001). Tables show properties of SMA line fits, between different variables and seed size. 
\clearpage

<<echo=FALSE,results='asis'>>=
Table03 <- read.csv("Table03_correlations_with_repro_inv.csv",
                    stringsAsFactors=FALSE, check.names=FALSE)
format_p <- function(p, digits = 4) {
  x <- as.character(round(p, digits = digits))
  pc <- 10^-digits
  x[p < pc] <- paste("<", pc)
  x
}

Table03$pval <- format_p(Table03$pval)
Table03$variable <- c("Total plant weight (mg)","Propagule investment (mg)","Fruit investment (mg)","Flower investment (mg)",
                      "Successful investment (mg)", "Successful pre-pollination investment (mg)","Provisioning investment (mg)",
                      "Failed tissues (mg)")
names(Table03) <- c("Variable", "n", "r$^2$", "p")
print(xtable(Table03,
               hline.after=c(1),
               align='p{0.1cm}p{6.5cm}p{1cm}p{1cm}p{1.5cm}',
               caption="Correlations with total reproductive investment",
             digits = 2),
               sanitize.text.function=I,
        , table.placement = "H"
        , caption.placement = "top"
        , include.rownames = FALSE
        , include.colnames = TRUE
        , size = "small"
        , floating = FALSE)
@

Table 3. Correlation of different estimates of reproductive investment (and total plant weight) against total reproductive investment (mg). Regressions are done across all individuals of all 14 study species for which both reproductive investment and the estimate variable are greater than zero. The total cost of failed tissues or simply the energy expenditure into flowers provides the best approximation of total reproductive investment. Flower investment is a composite variable calculated as flower weight (mg)*bud count. Successful investment is a composite variable calculated as seed costs (mg)*seed count.

>>>>

flowering_parts <- read.csv("Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)

@@

  plot(graph)
  #plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE); box()
}
@

@@

<<echo=FALSE, results='asis', warning=FALSE>>=

make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")

  yvar <- "repro_inv"
  xvar <- "propagule_inv"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
  results <- fit$groupsummary
  acc_slopes <- dplyr::select(results,group,n,r2,pval)
  names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")

  yvar <- "repro_inv"
  xvar <- "flower_inv"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
  results <- fit$groupsummary
  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
  acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  acc_slopes
}

TableSXX <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)

names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
TableSXX[,3] <- format(TableSXX[,3],digits=2,nsmall=2)
TableSXX[,6] <- format(TableSXX[,6],digits=2,nsmall=2)
TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
TableSXX[,4] <- format_p(TableSXX[,4])
TableSXX[,7] <- format_p(TableSXX[,7])

@@

### 2016-12-13 scripts/Accessory_figs_2015_12.Rmd
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

plot(total_accessory_Lord ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="total per seed accessory costs")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
summary(mod)
```

```{r}
plot(b_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
mod <- lm(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0),slope.test=1)
summary(slopes)

plot(c_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]],c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
mod <- lm(log(c_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,c_div_p>0.00001))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(c_div_p) ~ log(seed_size),data=subset(SummaryInd,c_div_p>0),slope.test=1)
summary(slopes)

@@

plot(total_accessory_Lord  ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
summary(slopes)

#calculation of total accessory investment divided by seed count (accessory_per_seed) very closely correlated with accessory costs per seed using the equations in Lord
plot(total_accessory_Lord  ~ accessory_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
summary(slopes)
summary(mod)

plot(seed_to_ovule_ratio ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seed_to_ovule_ratio),data=subset(SummaryInd,seed_to_ovule_ratio>0))
words.bottom.left.logxy(mod)

@@

>>>>

plot(total_accessory_Lord ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
words.bottom.right.logxy(mod)
summary(mod)

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
words.bottom.right.logxy(mod)
summary(mod)
```

```{r}
plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
mod <- lm(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(b_div_p) ~ log(seed_size),data=subset(SummaryInd,b_div_p>0),slope.test=1)
summary(slopes)

plot(c_div_p ~ seed_size,data=subset(SummaryInd,c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
mod <- lm(log(c_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,c_div_p>0.00001))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(c_div_p) ~ log(seed_size),data=subset(SummaryInd,c_div_p>0),slope.test=1)
summary(slopes)

@@

plot(total_accessory_Lord  ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
summary(slopes)
slopes2 <- as.matrix(coef(slopes))
abline(log(slopes2[1]),slopes2[2])
#calculation of total accessory investment divided by seed count (accessory_per_seed) very closely correlated with accessory costs per seed using the equations in Lord
plot(total_accessory_Lord  ~ accessory_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
summary(slopes)
summary(mod)

plot(seed_to_ovule_ratio ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")

plot(seedset ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seed_to_ovule_ratio),data=subset(SummaryInd,seed_to_ovule_ratio>0))
words.bottom.left.logxy(mod)

@@

par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(total_accessory_Lord ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
abline(0,1)
mod <- lm(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
words.bottom.right.logxy(mod)
summary(mod)

plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),col=col.spp(species),pch=16,log="xy")
abline(0,1)
mod <- lm(log(c_div_p) ~ log(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER",total_accessory_Lord>0))
words.bottom.right.logxy(mod)

plot(b_div_p ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
abline(1.1,1)
mod <- lm(log(b_div_p) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
words.bottom.right.logxy(mod)

plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
abline(0,1)
mod <- lm(log(dispersalcosts_increment) ~ log(seed_size),data=subset(SummarySpp[["mean"]],dispersalcosts_increment>0))
words.bottom.right.logxy(mod)

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "total_accessory_Lord"
yvar <- "RA"

data <- subset(SummaryInd,total_accessory_Lord>0&RA>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "total_accessory_Lord"
yvar <- "repro_inv"

data <- subset(SummaryInd,total_accessory_Lord>0&RA>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "b_div_p"
yvar <- "repro_inv"

data <- subset(SummaryInd,b_div_p>0&RA>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

#seedset lower in plants with bigger seeds, except at oldest site, when large seeded species doing relatively better and relationship flat
```{r}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==32),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==32))
words.bottom.left.logxy(mod)

plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==9),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==9))
words.bottom.left.logxy(mod)

plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==7),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==7))
words.bottom.left.logxy(mod)

plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==5),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==5&seedset>0))
words.bottom.left.logxy(mod)
```

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
abline(0,1)
plot(c_div_p ~ seed_size,data=subset(SummaryInd,species!="COER"),col=col.age(age),pch=16,log="xy")
abline(0,1)
plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
abline(0,1)
plot(total_accessory_Lord ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
```
